The Role of Variability in Learning Generalization: A Computational Modeling Approach

### 2024-04-15 Sections/full.qmd
make html version a bit nicer. Fix latex issue in alt pdf.

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
#subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
#date: 04/04/24
author:
- name: Thomas Gorman
  affiliation: Indiana University
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
cache: true
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
prefer-html: true
---

@@

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
#subtitle: "The Role of Variability in Learning Transfer: A Similarity-Based Computational Approach"
#date: 04/04/24
author:
- name: Thomas Gorman
  affiliation: Indiana University
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
prefer-html: true
---

@@

\normalsize
